On the discovery and origin of $r$-process stars in the Milky Way

### 2018-02-09 article/ms.tex

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Discovery and origin of $r$-process stars]{On the discovery and origin of $r$-process stars in the Milky Way}

@@

	The LAMOST giants we analyse belong to a broad range of metallicity ($-1.6 < \rm{[Fe/H]} < 0.6$), and don't cluster in any part of the sky, suggesting they do not belong to a single stellar system.

@@

			-               	& {[}H:M:S{]}   & {[}H:M:S{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$cm\ s^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.

\title[Discovery and origin of $r$-process stars]{On the discovery and origin of $r$-process stars in the Milky Way}

@@

	\subsection{Selection effects}
	The LAMOST giants we analyse belong to a broad range of metallicity ($-1.6 < \rm{[Fe/H]} < 0.6$), and don't cluster in any part of the sky, suggesting they do not belong to a single stellar system.

@@

			-               	& {[}H:M:S{]}   & {[}H:M:S{]}	& {[}$\rm{pixel}^{-1}${]} & {[}$\rm{km\ s}^{-1}${]} & {[}K{]}             	& {[}$\rm{cm\ s}^{-2}${]} & {[}dex{]}          	& {[}dex{]}              	& -                        	& {[}dex{]}        	& {[}dex{]}  	\\ \midrule
